---
title: "Final Study Data Analysis"
author: "April Kim, Jennifer Podracky, Saurav Datta"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(data.table)
library(lmtest)
library(pwr)
library(lsr)
library(effsize)
library(cobalt)
library(stringr)
library(AER)
library(stargazer)
```


##Read in data and reformat##
```{r}
assigned_treatment_seq <- data.frame(seq_id = c(1,2,3,4,5,6), 
                                     day1 = c(0,0,1,1,2,2),
                                     day2 = c(1,2,0,2,0,1),
                                     day3 = c(2,1,2,0,1,0))
d2 <- fread("241 Participant List - Final Study Results - 20181215.csv", na.strings=c("","NA"))
d2[UserId == 65,]$Q10 <- "In person"
d2[UserId == 13,]$Q6 <- "Through digital means"
d2$`Living Situation`[is.na(d2$`Living Situation`)] <- "Other"
d2$Age[is.na(d2$Age)] <- "Other"
d2$Q17[is.na(d2$Q17)] <- "Other"
# stringsAsFactors = F)
names(d2) <- str_replace_all(names(d2), c(" " = "." , "," = "" ))
# subset d2 for those who responded (Submitted.Data = 1)

# Not applicable = 0
# Through digital means = 1
# In person = 2
# Both in person and through digital means = 3

d2 <- d2[, .(userId = UserId,
             treatment_seq = factor(Treatment.Seq),
             day1_treatment = factor(Q6, levels = c('Not applicable', 'Through digital means', 'In person'),
                                                             labels = c(0, 1, 2)), 
             day2_treatment = factor(Q10, levels = c('Not applicable', 'Through digital means', 'In person'),
                                                             labels = c(0, 1, 2)),
             day3_treatment = factor(Q14, levels = c('Not applicable', 'Through digital means', 'In person'),
                                                             labels = c(0, 1, 2)),
             day1_steps = as.numeric(gsub("\\,", "", Q7)),
             day2_steps = as.numeric(gsub("\\,", "", Q11)),
             day3_steps = as.numeric(gsub("\\,", "", Q15)),
             age_range = factor(Age, levels = c('18 - 24', 
                                                "25 - 34",
                                                "35 - 44",
                                                "45 - 54",
                                                "55 - 64",
                                                "65+", "Other"),
                                labels = c(0, 1, 2, 3, 4, 5, 6)),
             # gender = factor(Gender),
             gender = factor(Gender, levels = c('Male', 'Female', 'Gender non-conforming'),
                                                     labels = c(0, 1, 2)),
             lives_with_others = factor(Living.Situation, levels = c('Alone', 'With others', "Other"),
                                                                labels = c(0, 1, 2)),
             # know_us = factor(Q17),
             know_us = factor(Q17, levels = c('No', 'Yes', "Other"),
                                                      labels = c(0, 1, 2)),
             location_lat = as.double(LocationLatitude),
             location_long = as.double(LocationLongitude),
             submitted_data = Submitted.Data
)]

head(d2, 5)

#Covariate Balance Check 1
bal.tab(as.numeric(treatment_seq) ~ gender + age_range + lives_with_others + know_us + location_lat + location_long, 
        data = d2)
cov_check <- glm(treatment_seq ~ gender + age_range + lives_with_others + know_us + location_lat + location_long, 
                data = d2, family = "binomial")
summary(cov_check)
```

```{r, results='asis'}
stargazer(cov_check, 
          dep.var.labels=c("Treatment sequence"),
          covariate.labels=c("Female", "Gender non-conforming", 
                             "Ages 25-34",
                             "Ages 35-44",
                             "Ages 45-54",
                             "Ages 55-64",
                             "Ages 65+", "Agest other",
                             "Has housemates", "Housemates unknown",
                             "Knows authors", "Knows authors unkonwn",
                             "Latitude", "Longitutde"),
          omit.stat=c("all"),
          single.row = TRUE)
```

## attrition check
```{r}
lm_attrit <- lm(submitted_data ~ treatment_seq + age_range + gender + lives_with_others + know_us + location_lat + location_long, data = d2)
summary(lm_attrit)
# know_us is highly predictive of whether or not people attrited. This makes sense.
```

```{r, results='asis'}
stargazer(lm_attrit, 
          dep.var.labels=c("Final survey submitted"),
          covariate.labels=c("Treatment Seq 2", "Treatment Seq 3", "Treatment Seq 4", "Treatment Seq 5", "Treatment Seq 6",
                             "Ages 25-34",
                             "Ages 35-44",
                             "Ages 45-54",
                             "Ages 55-64",
                             "Ages 65+", "Agest other",
                             "Female", "Gender non-conforming",
                             "Has housemates", "Housemates unknown",
                             "Knows authors", "Knows authors unkonwn",
                             "Latitude", "Longitutde"),
          omit.stat=c("all"),
          single.row = TRUE)
```

##Checking for ordering/priming effect AND adding non-compliant but okay users##
##Is previous day's treatment highly predictive of how many steps are taken today?##
```{r}
'%!in%' <- function(x,y)!('%in%'(x,y))

d2 <- d2[submitted_data == 1]

# n = 51
df1 <- d2

# remove subjects/rows who were non-compliant (n = 2)
# n = 49
df1 <- df1[rowSums(is.na(df1[,c(6:8)])) != ncol(df1[,c(6:8)]), ]

head(df1, 5)

# n = 30
d_followed_treatment_sequence <- rbindlist(list(subset(df1, treatment_seq == 1 & df1$day1_treatment == assigned_treatment_seq[1,2]
                                                       & df1$day2_treatment == assigned_treatment_seq[1,3]
                                                       & df1$day3_treatment == assigned_treatment_seq[1,4]),                            
                                                subset(df1, treatment_seq == 2 & df1$day1_treatment == assigned_treatment_seq[2,2]
                                                       & df1$day2_treatment == assigned_treatment_seq[2,3]
                                                       & df1$day3_treatment == assigned_treatment_seq[2,4]),
                                                subset(df1, treatment_seq == 3 & df1$day1_treatment == assigned_treatment_seq[3,2]
                                                       & df1$day2_treatment == assigned_treatment_seq[3,3]
                                                       & df1$day3_treatment == assigned_treatment_seq[3,4]),
                                                subset(df1, treatment_seq == 4 & df1$day1_treatment == assigned_treatment_seq[4,2]
                                                       & df1$day2_treatment == assigned_treatment_seq[4,3]
                                                       & df1$day3_treatment == assigned_treatment_seq[4,4]),
                                                subset(df1, treatment_seq == 5 & df1$day1_treatment == assigned_treatment_seq[5,2]
                                                       & df1$day2_treatment == assigned_treatment_seq[5,3]
                                                       & df1$day3_treatment == assigned_treatment_seq[5,4]),
                                                subset(df1, treatment_seq == 6 & df1$day1_treatment == assigned_treatment_seq[6,2]
                                                       & df1$day2_treatment == assigned_treatment_seq[6,3]
                                                       & df1$day3_treatment == assigned_treatment_seq[6,4])
))

# n = 19
d_not_followed_treatment_sequence <- subset(df1, userId %!in% d_followed_treatment_sequence$userId)

d_not_followed_but_ok <- subset(d_not_followed_treatment_sequence, d_not_followed_treatment_sequence$day1_treatment != d_not_followed_treatment_sequence$day2_treatment & 
                                  d_not_followed_treatment_sequence$day1_treatment != d_not_followed_treatment_sequence$day3_treatment &
                                  d_not_followed_treatment_sequence$day2_treatment != d_not_followed_treatment_sequence$day3_treatment)

na.omit(d_not_followed_but_ok)
d_not_followed_no_NA <- subset(d_not_followed_treatment_sequence, userId %!in% d_not_followed_but_ok$userId)
# n = 15
d_not_followed_no_NA <- na.omit(d_not_followed_no_NA)

# n = 33
df <- rbind(d_followed_treatment_sequence, d_not_followed_but_ok)
# n = 48
df2 <- rbind(d_followed_treatment_sequence, d_not_followed_but_ok, d_not_followed_no_NA)

# day 3 steps using day 1 and 2 treatment on complied + people who followed within subject design
m1 <- lm(day3_steps ~ day1_treatment + day2_treatment, df)
summary(m1)
# ATE (standard error)
print(paste0("Estimated effect of day1 treatment: ", signif(m1$coefficients[2], 3),
" (", signif(coef(summary(m1))[2,2], 3), ")"))
print(paste0("Estimated effect of day2 treatment: ", signif(m1$coefficients[3], 3),
" (", signif(coef(summary(m1))[3,2], 3), ")"))
# include days1,2 steps as covariates to understand
# subjects' step counts have as a function of
# treatment against waht they would typically do
m2 <- lm(day3_steps ~ day1_treatment + day2_treatment + day1_steps + day2_steps, df)
summary(m2)
print(paste0("Estimated effect of day1 treatment: ", signif(m2$coefficients[2], 3),
             " (", signif(coef(summary(m2))[2,2], 3), ")"))
print(paste0("Estimated effect of day2 treatment: ", signif(m2$coefficients[3], 3),
             " (", signif(coef(summary(m2))[3,2], 3), ")"))

# day 3 steps using day 1 and 2 treatment on complied + people who followed within subject design + rest who submitted data without any missing data
m1 <- lm(day3_steps ~ day1_treatment + day2_treatment, df2)
summary(m1)
# ATE (standard error)
print(paste0("Estimated effect of day1 treatment: ", signif(m1$coefficients[2], 3),
             " (", signif(coef(summary(m1))[2,2], 3), ")"))
print(paste0("Estimated effect of day2 treatment: ", signif(m1$coefficients[3], 3),
             " (", signif(coef(summary(m1))[3,2], 3), ")"))
# include days1,2 steps as covariates to understand
# subjects' step counts have as a function of
# treatment against waht they would typically do
m2 <- lm(day3_steps ~ day1_treatment + day2_treatment + day1_steps + day2_steps, df2)
summary(m2)
print(paste0("Estimated effect of day1 treatment: ", signif(m2$coefficients[2], 3),
             " (", signif(coef(summary(m2))[2,2], 3), ")"))
print(paste0("Estimated effect of day2 treatment: ", signif(m2$coefficients[3], 3),
             " (", signif(coef(summary(m2))[3,2], 3), ")"))
```
We do not see that the previous days' treatment assignments to predict the last day's step count is highgly predicitive and significant, which is super for us! 

```{r, results='asis'}
stargazer(m1, m2, 
          dep.var.labels=c("Steps - Day 3"),
          column.labels=c("Short", "Long"),
          covariate.labels=c("Digital - Day 1", "In person - Day 1", "Digital - Day 2", "In person - Day 2", "Steps - Day 1", "Steps - Day 2"),
          omit.stat=c("all"),
          single.row = TRUE)
```

##Condense treatment sequence to 1 treatment##
```{r}
df1.1 <- df[,-c(4,5,7,8)] 
df2.1 <- df[,-c(3,5,6,8)] 
df3.1 <- df[,-c(3,4,6,7)] 
names(df1.1)[names(df1.1) == "day1_treatment"] = "treatment"
names(df1.1)[names(df1.1) == "day1_steps"] = "steps"
names(df2.1)[names(df2.1) == "day2_treatment"] = "treatment"
names(df2.1)[names(df2.1) == "day2_steps"] = "steps"
names(df3.1)[names(df3.1) == "day3_treatment"] = "treatment"
names(df3.1)[names(df3.1) == "day3_steps"] = "steps"
d <- rbind(df1.1, df2.1, df3.1)
# combine digital and in person treatment as one
d$treatment2 <- ifelse(d$treatment == 0, 0, 1)
d$outcome <- ifelse(d$steps > 5000, 1, 0)

head(d, 5)

#Covariate Balance Check on treatment = 0,1,2
bal.tab(as.numeric(treatment) ~ gender + age_range + lives_with_others + know_us + location_lat + location_long,
       data = d)
cov_check1 <- glm(treatment ~ gender + age_range + lives_with_others + know_us + location_lat + location_long,
               data = d, family = "binomial")
summary(cov_check1)

#Covariate Balance Check on treatment = 0,1
bal.tab(as.numeric(treatment2) ~ gender + age_range + lives_with_others + know_us + location_lat + location_long,
       data = d)
cov_check2 <- glm(treatment2 ~ gender + age_range + lives_with_others + know_us + location_lat + location_long,
               data = d, family = "binomial")
summary(cov_check2)
```

```{r, results='asis'}
stargazer(cov_check2, cov_check1, 
          dep.var.labels=c("2 levels treatment", "3 levels treatment"),
          covariate.labels=c("Female",
                             "Ages 25-34",
                             "Ages 35-44",
                             "Ages 45-54",
                             "Ages 55-64",
                             "Ages 65+", 
                             "Has housemate", "Knows us","Latitute", "Longitude", "Constant"),          
          omit.stat=c("all"),
          single.row = TRUE)
```

##Make some pretty plots to show distribution, populatin etc. ##
```{r}
# population that actually responded to data collection survey
require(gridExtra)
d.gender <- d[, c("gender", "treatment2")]
p_gender <- ggplot(d.gender, aes(x=gender, fill = factor(treatment2))) + 
  geom_bar(stat="count", position=position_dodge()) +
  theme_minimal() + theme(legend.position="right",
                          panel.border = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
  xlab("") + ylab("") + ggtitle("Gender") +
  guides(fill = guide_legend(title = "Assignment")) +
  scale_fill_discrete(labels = c("Control", "Treatment")) +
  scale_x_discrete(breaks = c(0, 1, 2), 
                     labels = c('Male', 'Female', 'Gender\n non-conforming'))
# ggsave("gender.png", width = 5, height = 3.5, units = "in",dpi = 300)

p_gender_no_legend <- ggplot(d.gender, aes(x=gender, fill = factor(treatment2))) + 
  geom_bar(stat="count", position=position_dodge()) +
  theme_minimal() + theme(legend.position="right",
                          panel.border = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
  xlab("") + ylab("") + ggtitle("Gender") +
  # guides(fill = guide_legend(title = "Assignment")) +
  # scale_fill_discrete(labels = c("Control", "Treatment")) +
  scale_x_discrete(breaks = c(0, 1, 2), 
                     labels = c('Male', 'Female', 'Gender\n non-conforming'))


d.age <- d[, c("age_range", "treatment2")]
p_age <- ggplot(d.age, aes(x=age_range, fill = factor(treatment2))) + 
  geom_bar(stat="count", position=position_dodge()) +
  theme_minimal() + theme(legend.position="right",
                          panel.border = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) + 
  xlab("") + ylab("") + ggtitle("Age range") +
  guides(fill = guide_legend(title = "Assignment")) +
  scale_fill_discrete(labels = c("Control", "Treatment")) +
  scale_x_discrete(breaks = c(0, 1, 2, 3, 4, 5, 6 ), 
                   labels = c('18 - 24', 
                              "25 - 34",
                              "35 - 44",
                              "45 - 54",
                              "55 - 64",
                              "65+", "NA"))

d.others <- d[, c("lives_with_others", "treatment2")]
p_others <- ggplot(d.others, aes(x=lives_with_others, fill = factor(treatment2))) + 
  geom_bar(stat="count", position=position_dodge()) +
  theme_minimal() + theme(legend.position="right",
                          panel.border = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
  xlab("") + ylab("") + ggtitle("Lives with others") +
  guides(fill = guide_legend(title = "Assignment")) +
  scale_fill_discrete(labels = c("Control", "Treatment")) +
  scale_x_discrete(breaks = c(0, 1, 2), 
                     labels = c('Alone', 'With others', "NA"))
ggsave("other.png", width = 5, height = 3.5, units = "in",dpi = 300)


d.know_us <- d[, c("know_us", "treatment2")]
p_know_us <- ggplot(d.know_us, aes(x=know_us, fill = factor(treatment2))) + 
  geom_bar(stat="count", position=position_dodge()) +
  theme_minimal() + theme(legend.position="right",
                          panel.border = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
  xlab("") + ylab("") + ggtitle("Know us") +
  guides(fill = guide_legend(title = "Assignment")) +
  scale_fill_discrete(labels = c("Control", "Treatment")) +
  scale_x_discrete(breaks = c(0, 1), 
                     labels = c('No', 'Yes'))
ggsave("know.png", width = 5, height = 3.5, units = "in",dpi = 300)


grid.arrange(p_gender_no_legend, p_age, p_others, p_know_us,
             ncol = 2)


# control and digital and in person distribution 
dist3 <- ggplot(d, aes(x=treatment, y=steps, colour = factor(treatment))) +
geom_boxplot() + geom_jitter() +
geom_hline(yintercept=5000, linetype="dashed", color = "red") +
xlab("") + ylab("") + theme_bw() + 
   theme(axis.text.y = element_blank(), axis.ticks = element_blank()) 
    # scale_x_discrete(breaks = c(0, 1, 2), 
                     # labels = c('None', 'Digital', "In-person")) +
  # theme(legend.position="none")

# control and treatment (digital+in person) when time component removed
dist2 <- ggplot(d, aes(x=treatment2, y=steps, colour = factor(treatment2))) +
geom_boxplot() + geom_jitter() +
geom_hline(yintercept=5000, linetype="dashed", color = "red") +
xlab("") + ylab("Step counts") + theme_bw() + theme(axis.ticks.x = element_blank()) +
    scale_x_continuous(breaks = c(0, 1), 
                     labels = c('Control', 'Treatment')) +
  theme(legend.position="none")

grid.arrange(dist2, dist3,
             ncol = 2)

```


## For control vs digital and control vs in person ##
```{r}
# d$treatment <- factor(d$treatment)
d$userId <- factor(d$userId)
fit_3 <- lm(outcome ~ treatment + userId , d)
# se clustered based on userID
se_3 <- coeftest(fit_3, vcovHC(fit_3, type = 'HC', cluster = "userID"))

fit_3_covariates <- lm(outcome ~ treatment + age_range + gender + lives_with_others + know_us + location_lat + location_long, d)
# robust se
se_3_covariates <- sqrt(diag(vcovHC(fit_3_covariates, type = 'HC')))

# ATE (standard error)
print(paste0("Estimated effect of treatment (control, in person, digital): ", signif(fit_3$coefficients[2], 3),
" (", signif(se_3[2,2], 3), ")"))
print(paste0("Estimated effect of treatment (control, in person, digital) + covariates: ", signif(fit_3_covariates$coefficients[3], 3),
" (", signif(se_3_covariates[2], 3), ")"))

```


```{r, results='asis'}
stargazer(fit_3,
          se=list(se_3[,2]),
          omit = "userId",
          omit.labels = "Subject IDs ommitted",
          dep.var.labels=c("Steps > 5000"),
          covariate.labels=c('Digital commitment', 'In person commitment',"Constant"),
          omit.stat=c("all"),
          single.row = TRUE)

stargazer(fit_3,
          se=list(se_3[,2]),
          dep.var.labels=c("Steps > 5000"),
          covariate.labels=c('Digital commitment', 'In person commitment',"Constant"),
          omit.stat=c("all"),
          single.row = TRUE)
```

```{r, results='asis'}
stargazer(fit_3, fit_3_covariates, 
          se=list(se_3[,2], se_3_covariates),
                    omit = "userId",
          omit.labels = "Subject IDs ommitted",
          dep.var.labels=c("Steps > 5000"),
          column.labels = c("User ID", "Covariates"),
          covariate.labels=c('Digital commitment', 
                             'In person commitment',
                             "Ages 25-34",
                             "Ages 35-44",
                             "Ages 45-54",
                             "Ages 55-64",
                             "Ages 65+", 
                             "Female","Has housemate", 
                             "Knows us",
                             "Latitute", 
                             "Longitude", 
                             "Constant"),
          omit.stat=c("all"),
          single.row = TRUE)
```

## test hypothesis that telling others make it more likely to take >5000 steps (control vs treatment) ##
```{r}
#suppress intercept term
fit_2 <- lm(outcome ~ treatment2 + userId, d)
#  se clustered based on userID
se_2 <- coeftest(fit_2, vcovHC(fit_2, type = 'HC', cluster = "userID"))

fit_2_covariates <- lm(outcome ~ treatment2 + age_range + gender + lives_with_others + know_us + location_lat + location_long, d)
# robust se
se_2_covariates <- sqrt(diag(vcovHC(fit_2_covariates, type = 'HC')))

# ATE (standard error)
print(paste0("Estimated effect of treatment (control, treatment): ", signif(fit_2$coefficients[2], 3),
" (", signif(se_2[2], 3), ")"))

print(paste0("Estimated effect of treatment (control, treatment) + covariates: ", signif(fit_2_covariates$coefficients[2], 3),
" (", signif(se_2_covariates[2], 3), ")"))

```

```{r, results='asis'}
stargazer(fit_2,
          se=list(se_2[,2]),
          omit = "userId",
          omit.labels = "Subject IDs ommitted",
          dep.var.labels=c("Steps > 5000"),
          covariate.labels=c('Social commitment', "Constant"),
          omit.stat=c("all"),
          single.row = TRUE)

stargazer(fit_2,
          se=list(se_2[,2]),
          dep.var.labels=c("Steps > 5000"),
          covariate.labels=c('Social commitment', "Constant"),
          omit.stat=c("all"),
          single.row = TRUE)
```


```{r, results='asis'}
stargazer(fit_2, fit_2_covariates, 
          se=list(se_2[,2], se_2_covariates),
          omit = "userId",
          omit.labels = "Subject IDs ommitted",
          dep.var.labels=c("Steps > 5000"),
          column.labels = c("User ID", "Covariates"),
          covariate.labels=c('Social commitment',
                             "Ages 25-34",
                             "Ages 35-44",
                             "Ages 45-54",
                             "Ages 55-64",
                             "Ages 65+", 
                             "Female",
                             "Has housemate", 
                             "Knows us",
                             "Latitute", 
                             "Longitude", 
                             "Constant"),          
          omit.stat=c("all"),
          single.row = TRUE)



```

##power calculations##
.  
.  
.  
.  
.  
.  
```{r}
### power analysis
###  Control vs treatment (digital + in person)
# hedge's g
(cohen.d(d[treatment2 == 0]$outcome, d[treatment2 == 1]$outcome, na.rm = T, hedges.correction = T))
# cohen's d
effect_size <- cohensD(d[treatment2 == 0]$outcome, d[treatment2 == 1]$outcome)
#power we got from our experiment
pwr.t2n.test(n1 = nrow(d[treatment2 == 0,]), n2 = nrow(d[treatment2 == 1,]), d = effect_size, sig.level = 0.05)
# 80% powered test
pwr.t.test(power = 0.8, d = effect_size, sig.level = 0.05, type = "two.sample")

#
#
#
#
# ###  Control vs in person
# # since we fail to reject the null hypothesis, 
# # let's calculate number of subjects needed for 80% power
# effect_size_person <- cohensD(d[treatment == 0]$steps, d[treatment == 2]$steps)
# #power we got from our experiment
# pwr.t2n.test(n1 = nrow(d[treatment == 0,]), n2 = nrow(d[treatment == 2,]), d = effect_size_person, sig.level = 0.05)
# # 80% powered test
# pwr.t.test(power = 0.8, d = effect_size_person, sig.level = 0.05, type = "two.sample")


### extra plots
# day1
pd1 <- ggplot(df, aes(x=day1_treatment, y=day1_steps, colour = factor(day1_treatment))) +
  geom_boxplot() + geom_jitter() +
  geom_hline(yintercept=5000, linetype="dashed", color = "red") +
  xlab("") + ylab("Step counts") + theme_bw() +
  scale_x_continuous(breaks = c(0, 1, 2),
                     labels = c(0, 1, 2)) +
  # labels = c('Control', 'In person', 'Through digital means')) +
  theme(legend.position="none") + ggtitle("Step count - day 1")
# day2
pd2 <- ggplot(df, aes(x=day2_treatment, y=day2_steps, colour = factor(day2_treatment))) +
geom_boxplot() + geom_jitter() +
geom_hline(yintercept=5000, linetype="dashed", color = "red") +
xlab("") + ylab("Step counts") + theme_bw() +
    scale_x_continuous(breaks = c(0, 1, 2),
                       labels = c(0, 1, 2)) +
    #                  labels = c('Control', 'In person', 'Through digital means')) +
  theme(legend.position="none") + ggtitle("Step count - day 2")
# day3
pd3 <- ggplot(df, aes(x=day3_treatment, y=day3_steps, colour = factor(day3_treatment))) +
geom_boxplot() + geom_jitter() +
geom_hline(yintercept=5000, linetype="dashed", color = "red") +
xlab("") + ylab("Step counts") + theme_bw() +
    scale_x_continuous(breaks = c(0, 1, 2),
                       labels = c(0, 1, 2)) +
    #                  labels = c('Control', 'In person', 'Through digital means')) +
  theme(legend.position="none") + ggtitle("Step count - day 3")




```




